\textsf{Are large language models superhuman chemists?}

### 2024-10-18 src/tex/sections/human_subset_selection.tex
Update human_subset_selection.tex
Update src/tex/sections/human_subset_selection.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\paragraph{Human subset selection}

For selecting a human subset, several design choices have been made. Firstly, from the full dataset, we keep all the questions that are labeled as advanced. In this way, we can obtain a deeper insight about the capabilities of LLMs on advanced task
when compared to actual chemists. Secondly, we sample a maximum of 3 questions across all possible combinations of categories (i.e., knowledge or reasoning) and topics (e.g., organic chemistry, physical chemistry). Thirdly, we do not include any intuition questions
in this subset. In total, 248 questions have been sampled for the human study. Then, this subset is divided into 2 subsets based on the aforementioned combinations. One of the question subsets allows tool use, and the other does not.

>>>>

\paragraph{Question selection}

Several design choices were made when selecting a human subset. Firstly, from the full dataset, we keep all the questions that are labeled as advanced. In this way, we can obtain a deeper insight about the capabilities of \glspl{llm} on advanced tasks
when compared to actual chemists. Secondly, we sample a maximum of 3 questions across all possible combinations of categories (i.e., knowledge or reasoning) and topics (e.g., organic chemistry, physical chemistry). Thirdly, we do not include any intuition questions
in this subset. In total, 248 questions have been sampled for the human study. Then, this subset is divided into 2 subsets based on the aforementioned combinations. One of the question subsets allows tool use, and the other does not.
